### 2023-02-13 chapters/interpretability/imli/appendix.tex
added appendix
imli new results

\section*{Appendix}

In the following, we present representative CNF classifiers learned in different datasets. In each dataset, if an input satisfies the CNF formula, it is predicted class $ 1 $ and vice-versa.

>>>>

\chapter{Interpretable Classification Rules}

\begin{figure}
	\centering
	\includegraphics[scale=0.38]{figures/interpretability/imli/thesis_exp/thesis_exp_cactus_train_val_fit_time}
	\includegraphics[scale=0.38]{figures/interpretability/imli/thesis_exp/thesis_exp_cactus_predicate_count}
	\includegraphics[scale=0.38]{figures/interpretability/imli/thesis_exp/thesis_exp_cactus_test_accuracy}
	\includegraphics[scale=0.38]{figures/interpretability/imli/thesis_exp/thesis_exp_cactus_train_val_accuracy}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.27]{figures/interpretability/imli/thesis_exp/thesis_exp_Parkinsons_cactus_train_val_fit_time}	\includegraphics[scale=0.27]{figures/interpretability/imli/thesis_exp/thesis_exp_WDBC_cactus_train_val_fit_time}	\includegraphics[scale=0.27]{figures/interpretability/imli/thesis_exp/thesis_exp_Pima_cactus_train_val_fit_time}	\includegraphics[scale=0.27]{figures/interpretability/imli/thesis_exp/thesis_exp_Titanic_cactus_train_val_fit_time}	\includegraphics[scale=0.27]{figures/interpretability/imli/thesis_exp/thesis_exp_Magic_cactus_train_val_fit_time}	\includegraphics[scale=0.27]{figures/interpretability/imli/thesis_exp/thesis_exp_Tom's_HW_cactus_train_val_fit_time}		\includegraphics[scale=0.27]{figures/interpretability/imli/thesis_exp/thesis_exp_Credit_cactus_train_val_fit_time}	\includegraphics[scale=0.27]{figures/interpretability/imli/thesis_exp/thesis_exp_Adult_cactus_train_val_fit_time}
\end{figure}

\section{Representative Interpretable Classification Rules in Datasets}
In the following, we present representative CNF classifiers learned in different datasets. In each dataset, if an input satisfies the CNF formula, it is predicted class $ 1 $ and vice-versa.
